### 2021-05-12 README.Rmd
Add instructions for reproducibility to readme

# Code for Look-Ahead Screening Rules Paper

@@

>>>>

# Code for the Hessian Screening Rule

@@

## Results

The results from the simulations, which were run
on a dedicated HPC cluster, are stored in the [results folder](results/).
The figures
in the paper, generated from these results, are stored
in [`figures/`](figures/).

## Reproducing the Results

The results from our paper were run through a singularity container. Check
the releases for pre-built singularity containers that you can download and use.

To reproduce the results, **always** use the
singularity container. To run an experiment from the
singularity container, call

```shell
singularity run --bind results:/Project/results container.sif <script>
```

where `<script>` should be a name of a script in the
[experiments folder](experiments/), such as `experiments/simulateddata.R`.

### Re-building the Singularity Container

If you want to re-build the singularity container from scratch (or
simply want to clone the repo to your local drive), you can
do so via the following steps.

1. Clone the repository to your local hard drive. On linux, using
   SSH authentication, run

   ```shell
   git clone git@github.com:jolars/LookAheadScreening.git
   ```

2. Navigate to the root of the repo and
   build the singularity container by calling

   ```shell
   cd LookAheadScreening
   sudo singularity build container.sif Singularity
   ```

Then proceed as in [Reproducing the Results](#reproducing-the-results)
to run the experiments.

### Running Experiments without Singularity (Not Recommended!)

Alternatively, you may also reproduce the results by cloning this repository
and starting
R in the root directory of this folder (which will activate the renv
repository) and then run

```r
renv::restore()
```

to restore the project library. Then build the R package (see below) and run the
simulations directly by running the scripts in the experiments folder. This
is **not recommended**, however, since it, unlike the Singularity
container approach, does not exactly
reproduce the software environment
used when these simulations where originally run and may result in
discrepancies due to differences in for instance operating systems,
compilers, and BLAS/LAPACK implementations.

## R Package

If you want to build
and experiment with the package, you can do so by calling

```shell
 R CMD INSTALL  .
```

provided you have `cd`ed to the root folder of this repository. First
ensure, however, that you have enabled the renv project library by calling
`renv::restore()` (see the section above).

## Data

The datasets used in these simulations are stored in the [data folder](data/).
Scripts to retrieve these datasets from their original
sources can be found in [`data-raw/`](data-raw/).
